\section{Project meetings}\label{sec:meetings}

We plan to have team meetings every week to plan the work for the upcoming week and review the progress of the past week as well as our overall project status and progress. These meetings do not require every team member to attend every single week. Depending on the workload in the specific weeks, the meetings can either focus on the project work or some leisure activities, or both.
\\\\
The further we move on with the project, the less discussions we expect in the meeting. As we are a large group of seven members, we want to keep the meetings almost exclusively organisational and only discuss urgent and important matters that truly concern everyone in the team. The work on the project is done in smaller groups to ensure productivity.
\\\\
In addition, we will meet with our customers once per week during the first month of the project as we have to gather a lot of information and discuss a lot of topics and decisions in the beginning. We will then switch to bi-weekly meetings afterward and finally to monthly meetings in the end as the topics under discussion will get less the more we progress with and dive into the project. Regarding certain deadlines, we will most likely have additional ad-hoc meetings with our customers to discuss e.g. the requirements. Again, these meetings do not necessarily require the attendance of all team members every time, but rather certain roles to take part. We also agreed with our customers to prepare these meetings with an agenda beforehand as required by the course.

\section{Time tracking}\label{sec:time-tracking}

For now, we created a table sheet for everyone to keep their working hours for the project per day updated. In the future, especially when we start to work on different topics, we want to integrate the time tracking into our Scrum tool framework and find a more intuitive tool for the purpose with the possibility to categorize the job types.
